% !TEX program = xelatex

\documentclass{resume}
\usepackage{hyperref}
\usepackage{enumitem}

\hyphenpenalty=8000

\begin{document}
\pagenumbering{gobble} % suppress displaying page number
\name{Mira (Han) Min}

\basicInfo{
	\email{min.han@northeastern.edu} \textperiodcentered\
	\phone{+1 (408)887-7859} \textperiodcentered\
	\linkedin[han-min]{https://www.linkedin.com/in/han-min}
}

\section[Education]{\faGraduationCap\ Education}
\datedsubsection{\textbf{Northeastern University}}{September 2022 - Present}
\vspace{1pt}
M.S. in Computer Science, \textbf{GPA: 4.00/4.00}
\vspace{1pt}

{\small \textbf{Relevant Coursework:}} Intensive Foundations of Computer Science\spliter Discrete Mathematics\spliter Object-Oriented Design\spliter Data Structures\spliter Algorithms\spliter Web Development
\vspace{0.3em}
\datedsubsection{\textbf{Zhongnan University of Economics and Law}}{September 2016 -  June 2020}
\vspace{1pt}
B.S. in Economics (Taxation), \textbf{GPA: 3.59/4.00}
\vspace{1pt}

{\small \textbf{Relevant Coursework:}} Calculus\spliter Probability Theory and Mathematical Statistics\spliter Linear Algebra\spliter Statistics\spliter Computer Application Foundation\spliter Database Application\spliter Literature Information Retrieval and Utilization\spliter Econometrics\spliter Tax Experiments

\section[Projects]{\faProjectDiagram\ Projects}

\subsection{\textbf{PetTalks: Social Media Platform for Pet Lovers}}
\vspace{-2pt}
\textit{Technologies:} React, JavaScript, Node.js, MySQL, Material UI
\vspace{-2pt}
\begin{itemize}[noitemsep]
    \item Developed a robust social media platform using \textbf{React} and \textbf{Node.js}, which includes content posting, user engagement,and recommendation features.
    \item Launched the product using \textbf{AWS} and \textbf{docker} and attracted over 100 registered users.
    \item Added searching functionalities by pet, by content, by user on the platform, enhancing user search efficiency and improving user experience.
\end{itemize}

\subsection{\textbf{AutoMarketInsights: Used Car Price Analysis Web Application}}
\vspace{-2pt}
\textit{Technologies:} Python, Pandas, React, Node.js, Selenium
\vspace{-2pt}
\begin{itemize}[noitemsep]
	\item Constructed a  \textbf{web crawler} using  \textbf{Python} and  \textbf{Selenium} to aggregate car listings from multiple websites such as CarMax and CarFax, collecting over 100,000 unique entries.
	\item Analyzed data with  \textbf{Pandas} to identify used cars' price trends in US, building a dashboard using  \textbf{Tableau} to visualize the trends in different conditions.
\end{itemize}

\subsection{\textbf{Calendar Master: A Google Calendar-like Android App}}
\vspace{-2pt}
\textit{Technologies:} Android, Java, Node.js, MongoDB
\vspace{-2pt}
\begin{itemize}[noitemsep]
    \item Developed an Android application in  \textbf{Java} to manage all kinds of meetings, helping the users to easily organize their life events and work planning.
    \item Designed a user-friendly interface for the users, providing them with conflicts resolution and smart meeting planning assistance.
    \item Integrated a data serialization system using  \textbf{JSON} and a  \textbf{Node.js} backend with  \textbf{MongoDB}, enabling seamless cross-device synchronization and data backup.
\end{itemize}

\subsection{\textbf{ArrayBoost: High-Performance Python Computing Engine with C++ Backend}}
\vspace{-2pt}
\textit{Technologies:} Python, C++, Cython
\vspace{-2pt}
\begin{itemize}[noitemsep]
\item Engineered a  \textbf{Python} computing engine with a  \textbf{C++} backend, providing a 20x performance boost to handle complex computations.
\item Developed a  \textbf{Python API} using  \textbf{Cython}, allowing developers to easily access the engine’s capabilities while leveraging improved performance.
\end{itemize}

\section[Skills]{\faCogs\ Skills}
\begin{itemize}
\item \textbf{Programming Languages:} Python, JavaScript, Java, C++
\item \textbf{Technologies} Node.js, HTML/CSS, React, Angular, jQuery, Bootstrap, Material UI, Git, Docker, Selenium, Markdown
\item \textbf{Databases:} MongoDB, MySQL
\item \textbf{Data Analysis:} Pandas, NumPy
\end{itemize}

\end{document}
